Computational methods in landscape ecology

### 2024-11-19 Manuscript.qmd
Adjust abstract
Update README

\noindent All authors contributed particular sections to the manuscript and assisted with the revision. Overall coordination, first and revised draft was led by MHKH.
Correspondence to [mhk.hesselbarth@gmail.com](mailto:mhk.hesselbarth@gmail.com)

@@

This review provides an overview of recent developments in computational methods that have advanced the research field of landscape ecology.
We focus on key topics such as spatial patterns, connectivity, simulations and modeling, landscape genetics, and spatial planning.

>>>>

\noindent All authors contributed particular sections to the manuscript and assisted with the revision. Overall coordination, first and revised draft was led by MHKH.
Correspondence to [mhk.hesselbarth@gmail.com](mailto:mhk.hesselbarth@gmail.com).

@@

This review provides an overview of recent developments in computational methods that have advanced the research field of landscape ecology.
We focus on key topics such as spatial patterns, connectivity, landscape genetics, sampling, simulations and modeling, and spatial planning.
